%-------------------------
% Variant: SIDEBAR (AltaCV / Two-Column)
% Left sidebar with contact/skills/education, right main column
%-------------------------
\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.4in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage{paracol}
\usepackage{needspace}

\definecolor{accent}{HTML}{1F2A44}
\definecolor{sidebarbg}{HTML}{F4F5F8}
\definecolor{soft}{HTML}{555B6E}

\RaggedRight
\hyphenpenalty=10000
\exhyphenpenalty=10000
\tolerance=1000
\emergencystretch=3em

\pagestyle{empty}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% Section formatting
\titleformat{\section}
  {\color{accent}\large\bfseries\scshape}{}{0em}{}[\vspace{1pt}{\color{accent}\hrule height 0.6pt}\vspace{1pt}]
\titlespacing*{\section}{0pt}{6pt}{2pt}

\titleformat{\subsection}
  {\color{accent}\normalsize\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{4pt}{1pt}

\setlist[itemize]{leftmargin=12pt, itemsep=1pt, parsep=0pt, topsep=1pt, label={\color{accent}\textbullet}}

\columnratio{0.30}
\setlength{\columnsep}{18pt}
\setlength{\columnseprule}{0pt}

\newcommand{\role}[3]{%
  \needspace{4\baselineskip}%
  {\bfseries #1}\hfill{\color{soft}\small #3}\\
  {\color{soft}\itshape #2}\\[1pt]
}

\begin{document}

% ============== HEADER ==============
\noindent
{\fontsize{28pt}{30pt}\selectfont\color{accent}\bfseries Alan Wrya}\\[2pt]
{\small\color{soft} Final-year Financial Mathematics Co-op Student}

\vspace{8pt}
{\color{accent}\hrule height 1pt}
\vspace{6pt}

% ============== TWO COLUMNS ==============
\begin{paracol}{2}

% -------- LEFT SIDEBAR --------
\section*{Contact}
\small
Toronto, ON\\[2pt]
\href{mailto:alan.wrya@torontomu.ca}{alan.wrya@torontomu.ca}\\[2pt]
(416) 939-5417\\[2pt]
\href{https://www.linkedin.com/in/alan-w-499547298/}{linkedin.com/in/alan-w}\\[2pt]
\href{https://github.com/left-nullspace}{github.com/left-nullspace}

\section*{Education}
\noindent\textbf{Toronto Metropolitan University}\\[1pt]
{\small\itshape\color{soft} Sept 2022 -- June 2026}\\[2pt]
BSc, Financial Mathematics Co-op\\
Computer Science Minor\\[2pt]
\textbf{CGPA: 3.81}\\
Dean's List Scholar\\[2pt]
{\small\itshape\color{soft}Coursework:} Stochastic Calculus, PDEs, Investment Analysis, Managerial Finance, Probability \& Statistics, Linear Algebra, Differential Equations, Data Structures

\section*{Skills}
\subsection*{Programming}
\small Python (Pandas, NumPy, Scikit-learn, Statsmodels), SQL, MATLAB, R, Java, VBA

\subsection*{Quantitative \& Finance}
\small Mean-variance optimization, Monte Carlo, Black-Scholes, Value-at-Risk, backtesting, time-series analysis, clustering, PCA

\subsection*{Tools}
\small Adobe Analytics, Excel (LAMBDA, dynamic ranges, VBA macros), PowerPoint, Git, Jupyter

\subsection*{AI / Agentic Workflows}
\small Claude, Codex, GitHub Copilot --- agentic code generation, research, automation

\section*{Activities}
\noindent\textbf{Math Tutor (Self-Employed)}\\[1pt]
{\small\itshape\color{soft} Sept 2022 -- Present}\\[2pt]
\small One-on-one tutoring in high-school calculus, algebra, trigonometry, and geometry; built customized lesson plans tailored to each student's learning style and academic goals.

% -------- RIGHT MAIN COLUMN --------
\switchcolumn

\section*{Summary}
Final-year Financial Mathematics Co-op student passionate about trading, financial markets, and quantitative research. Hands-on experience across bank-side analytics (TD Direct Investing), portfolio research (cluster-constrained MV optimization), and trading-software development (Anomalies platform).

\section*{Experience}
\role{TD Bank}{Co-op, Direct Investing Journey Analyst}{Jan 2025 -- Aug 2025}
\begin{itemize}
  \item Rebuilt 12+ monthly KPI dashboards in Excel using VBA, LAMBDA functions, dynamic named ranges, and reusable chart templates, reducing manual refresh time from 2-5 hours per week to under 5 minutes per dashboard.
  \item Engineered automated 24-month rolling performance charts with dynamic labels and auto-scaling axes, enabling leadership to refresh reports on demand and standardize reporting across the team.
  \item Built client segmentation frameworks and ran correlation and regression analysis on three years of monthly client data to surface drivers of retention, funding, and engagement.
  \item Led analytics tagging plans for new Direct Investing features: reviewed wireframes, scoped high-value events, presented to tagging and analytics teams, and coordinated risk sign-off across product, analytics, and 1B controls.
  \item Ran feature-launch lookback analyses on enhanced search adoption and mobile vs.\ desktop trading behaviour in Adobe Analytics and Excel to inform roadmap prioritization and executive-facing recommendations.
  \item Took on expanded analytics, stakeholder, and reporting responsibilities during the manager's parental leave.
\end{itemize}

\role{Ted Rogers Sales \& Trading (TRST)}{Quantitative Analyst}{Sept 2023 -- Dec 2025}
\begin{itemize}
  \item Built a Portfolio Optimization \& Simulation tool using historical data and mean-variance optimization to generate optimal Sharpe and minimum-volatility portfolios.
  \item Developed a Value-at-Risk tool using Monte Carlo simulations to assess potential portfolio losses from a distribution of outcomes.
  \item Adapted an interactive Black-Scholes option pricing calculator to compute call/put prices, implied volatility, and probabilities of expiring in-the-money.
\end{itemize}

\role{R\&R Utility Limited}{Project Management Assistant}{Sept 2021 -- Apr 2024}
\begin{itemize}
  \item Supported the development of corporate operating budgets, project costing, and drawdown budgets across multi-discipline engineering and construction projects.
  \item Ran financial reconciliations on vendor invoices to resolve billing discrepancies and improve cost-tracking accuracy.
\end{itemize}

\section*{Research \& Projects}
\role{Cluster-Constrained Portfolio Optimization}{Python, Scikit-learn}{2025 -- 2026}
\begin{itemize}
  \item Researched whether sector-clustering constraints improve mean-variance portfolio performance vs.\ plain MV on a 33-stock sector-stratified universe.
  \item Built an end-to-end backtesting pipeline: Ward hierarchical clustering $\rightarrow$ cluster-constrained MV optimization $\rightarrow$ benchmarking against Plain MV and ERC across 860 rolling 5-year windows.
  \item Showed cluster-constrained MV matches plain MV's out-of-sample Sharpe while materially lowering portfolio concentration, max drawdown, and 5\% expected shortfall.
  \item Identified that plain MV behaves as an \emph{error maximizer}, concentrating allocations in in-sample winners; cluster constraints mitigate this without sacrificing risk-adjusted returns.
\end{itemize}

\role{Anomalies: Point-and-Click Trading Strategy Discovery Platform}{Python, DEAP, vectorbtpro, PySide6}{2025 -- Present}
\begin{itemize}
  \item Core builder on a small team developing a point-and-click desktop application that lets users design, backtest, and stress-test systematic trading strategies across crypto and equity markets.
  \item Designed and built the backtesting engine, stress-testing pipeline, and evolutionary search system (DEAP) that discovers novel strategies by exploring combinations of technical-indicator signals and exit parameters.
  \item Built the desktop UI (PySide6) and a multi-source market data layer (Yahoo Finance, Binance, dYdX, Paradex, Hyperliquid) with local SQLite caching and Turso cloud sync.
\end{itemize}

\end{paracol}

\end{document}
