%-------------------------
% Resume — Alan Wrya
% Compile: tectonic resume.tex
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[margin=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{charter}              % cleaner, more modern serif
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{microtype}            % better justification / kerning
\usepackage{ragged2e}

% --- Color palette ---
\definecolor{accent}{HTML}{1F2A44}     % deep slate
\definecolor{rule}{HTML}{C9CCD3}       % light rule

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\setlength{\tabcolsep}{0in}

\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
    pdftitle={Alan Wrya — Resume},
    pdfauthor={Alan Wrya}
}

% --- Section formatting ---
\titleformat{\section}
  {\vspace{2pt}\color{accent}\scshape\raggedright\Large\bfseries}
  {}{0em}{}
  [\vspace{-2pt}{\color{rule}\titlerule[0.8pt]}\vspace{-4pt}]
\titlespacing*{\section}{0pt}{8pt}{4pt}

% --- Custom commands ---
\newcommand{\resumeItem}[1]{%
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{%
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{%
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & {\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=1pt, parsep=0pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}


%==========================================================
\begin{document}

%-----------HEADER-----------
\begin{center}
    {\fontsize{26pt}{30pt}\selectfont \color{accent} \scshape \textbf{Alan Wrya}} \\ \vspace{6pt}
    \small
    Toronto, ON \;\textbullet\;
    \href{mailto:alan.wrya@torontomu.ca}{alan.wrya@torontomu.ca} \;\textbullet\;
    (416) 939-5417 \\
    \href{https://www.linkedin.com/in/alan-w-499547298/}{linkedin.com/in/alan-w} \;\textbullet\;
    \href{https://github.com/left-nullspace}{github.com/left-nullspace}
\end{center}
\vspace{-6pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Toronto Metropolitan University}{Toronto, ON}
      {Bachelor of Science (BSc), Financial Mathematics Co-op \;$|$\; Computer Science Minor}{Sept 2022 -- June 2026}
    \resumeItemListStart
      \resumeItem{\textbf{CGPA: 3.95} \;$|$\; Dean's List Scholar (all eligible terms)}
      \resumeItem{\textit{Relevant Coursework:} Stochastic Calculus, Partial Differential Equations, Investment Analysis, Managerial Finance, Probability \& Statistics, Linear Algebra, Differential Equations, Data Structures, Computer Science}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {TD Bank --- Direct Investing}{Jan 2025 -- Aug 2025}
      {Co-op, Direct Investing Journey Analyst}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Rebuilt 12+ monthly KR/OKR dashboards in Excel using \textbf{VBA}, LAMBDA functions, dynamic named ranges, and reusable chart templates --- cutting manual refresh time from 2--5 hours per week to under 5 minutes per tab.}
        \resumeItem{Engineered automated 24-month rolling performance charts with dynamic labels, $\pm 3\sigma$ control limits, and auto-scaling axes, enabling leadership to refresh reports on demand and standardize reporting across the team.}
        \resumeItem{Built client segmentation frameworks (Core Funded, Newly Funded, Reactivated, Attrited) and conducted correlation/regression analysis on 3 years of monthly client data to identify drivers of retention, funding, and engagement.}
        \resumeItem{Led analytics tagging plans for new Direct Investing features --- reviewed wireframes, scoped high-value events, presented to tagging/analytics teams, and coordinated risk sign-off across product, analytics, and 1B controls.}
        \resumeItem{Conducted feature-launch lookback analyses (e.g.\ enhanced search adoption, mobile vs.\ desktop trading behaviour) in Adobe Analytics and Excel to inform roadmap prioritization and executive-facing recommendations.}
        \resumeItem{Took on expanded analytics, stakeholder, and reporting responsibilities during the manager's parental leave.}
      \resumeItemListEnd

    \resumeSubheading
      {Ted Rogers Sales \& Trading (TRST)}{Sept 2023 -- Dec 2025}
      {Quantitative Analyst}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Built a \textbf{Portfolio Optimization \& Simulation tool} using historical data and mean-variance optimization to generate optimal Sharpe and minimum-volatility portfolios.}
        \resumeItem{Developed a \textbf{Value-at-Risk tool} using Monte Carlo simulations to assess potential portfolio losses from a distribution of outcomes.}
        \resumeItem{Adapted an interactive Black-Scholes option pricing calculator to compute call/put prices, implied volatility, and probabilities of expiring in-the-money.}
      \resumeItemListEnd

    \resumeSubheading
      {R\&R Utility Limited}{Sept 2021 -- Apr 2024}
      {Project Management Assistant}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Supported development of corporate operating budgets, project costing, and drawdown budgets across multi-discipline engineering and construction projects.}
        \resumeItem{Conducted financial reconciliations on vendor invoices, resolving billing discrepancies and improving cost tracking accuracy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------RESEARCH & PROJECTS-----------
\section{Research \& Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Cluster-Constrained Portfolio Optimization} (Undergraduate Thesis) \;$|$\; \emph{Python, Scikit-learn}}{2025 -- 2026}
      \resumeItemListStart
        \resumeItem{Researched whether sector-clustering constraints improve mean-variance portfolio performance vs.\ plain MV on a 33-stock sector-stratified universe.}
        \resumeItem{Built an end-to-end backtesting pipeline: Ward hierarchical clustering $\rightarrow$ cluster-constrained MV optimization $\rightarrow$ benchmarking against Plain MV and ERC across 860 rolling 5-year windows.}
        \resumeItem{Demonstrated cluster-constrained MV consistently outperforms plain MV out-of-sample across weekly and monthly rebalancing horizons.}
        \resumeItem{Showed plain MV behaves as an \emph{error maximizer} --- concentrating allocations in in-sample winners and underperforming out-of-sample.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Anomalies Research --- Systematic Equity Strategies} \;$|$\; \emph{Python, Pandas, NumPy}}{2025 -- Present}
      \resumeItemListStart
        \resumeItem{Designed and built the end-to-end backtesting framework and stress-testing pipeline used to evaluate systematic equity anomalies.}
        \resumeItem{Engineered modular logic for signal generation, portfolio construction, and out-of-sample validation --- enabling rapid iteration across new strategy ideas.}
        \resumeItem{Implemented robustness checks including drawdown analysis, regime testing, and parameter-sensitivity stress tests.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Clustering-Based Selection for Investment Portfolios} \;$|$\; \emph{Python, Scikit-learn, PCA, k-means}}{Jul 2024}
      \resumeItemListStart
        \resumeItem{Built an unsupervised-learning tool to cluster ETFs and strategies by market correlation and risk-adjusted return features; applied PCA + k-means.}
        \resumeItem{Validated that near-zero correlation between top selected strategies from each cluster held up in out-of-sample testing.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{ETF SQL Database Management System} \;$|$\; \emph{Python, SQLAlchemy, SQLite, yfinance}}{Aug 2024}
      \resumeItemListStart
        \resumeItem{Designed a Python tool to manage ETF/stock data via SQLite and SQLAlchemy, with incremental updates that fetch only data past the maximum existing date --- reducing API requests and runtime by \textbf{over 95\%} vs.\ full reload.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Programming:} Python (Pandas, NumPy, Scikit-learn, Statsmodels, SQLAlchemy), SQL, MATLAB, R, Java, VBA \\
        \textbf{Quantitative \& Finance:} Mean-variance optimization, Monte Carlo simulation, Black-Scholes, Value-at-Risk, backtesting, time-series analysis, clustering, PCA \\
        \textbf{Tools:} Adobe Analytics, Excel (advanced --- LAMBDA, dynamic ranges, VBA macros), PowerPoint, Git, Jupyter
    }}
\end{itemize}


%-----------ACTIVITIES-----------
\section{Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Math Tutor (Self-Employed)}{Sept 2022 -- Present}
      {Private High School Mathematics Instruction}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{One-on-one tutoring in algebra, calculus, geometry, and trigonometry; built customized lesson plans tailored to individual students' learning styles and academic goals.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\end{document}
